---
title: Posterior medial network dynamics, CamCan movie watching - Replication Sample
author: Rose Cooper
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    theme: cerulean
    toc: true
    toc_float:
      collapsed: false
---

These analyses investigate connectivity dynamics of the posterior medial network (PMN) during a movie-watching task. The data includes 136 younger adults (age 18-40) (68 for the initial 'discovery' analyses, 68 for replication) from the [CamCan dataset](https://www.cam-can.org/index.php?content=dataset).  

Each PMN region is a cluster of 100 contiguous voxels (2x2x2mm) within the Default A and C subnetworks ([Schaefer et al., 2018](https://github.com/ThomasYeoLab/CBIG/tree/master/stable_projects/brain_parcellation/Schaefer2018_LocalGlobal)) that activate during 'episodic' tasks (according to the NeuroSynth meta analysis) - based on the definition in [Ritchey & Cooper (2020, TiCS)](https://www.sciencedirect.com/science/article/pii/S1364661320300814).   

The analyses first test time-averaged functional connectivity, so the pearson correlation (and partial correlation) between ROI time series during the full movie watching task. I use this to investigate the presence of subsystems (from seed-to-voxel analyses) and intranetwork connectivity.  

Next, the analyses test time-varying connectivity of the PMN subsystems in relation to the movie content (similarity across subjects), including change in connectivity at event transitions.  

# Setup
```{r, warning=FALSE, message=FALSE}

library(tidyverse)
library(plotly)
library(ggnetwork)
library(cowplot)
library(ggpubr)
library(knitr)
library(psych)
library(rstatix)
library(reshape2)
library(pracma)
library(mosaic)
library(NetworkToolbox)
library(pander)
library(lessR)
library(fmri)
library(ppcor)
library(corpcor)
library(network)
library(GGally)
library(igraph)
library(tidygraph)
library(lsa)
library(prodlim)
library(stringr)
library(caret)
library(abind)


## define sample to analyze (discovery or replication)
this.group <- "Replication"
cat(this.group,'sample')

```

**R package information**
```{r}
sessionInfo()
```

Define custom functions & color palettes  
```{r}

### define functions:
se <- function(x) sqrt(var(x)/length(x))  #function to calculate SE
ci <- function(x) (sqrt(var(x)/length(x))) * 1.96  #function to calculate 95% CI

### color palettes:
# color my 8 nodes
mycolors = c('#f2a68c','#929292','#e6664d','#8ce9f7','#3c7ff5','#934be0','#fcd841','#95df3a')
module.colors <- c("#fcd841","#3c7ff5","#8ce9f7")  #for "Dorsal PM", "Ventral PM", "Ventral PM-to-Dorsal PM"

# color scales
gray.colors  <- colorRampPalette(c("gray90","gray10"))
heat.colors  <- colorRampPalette(c("#009FFF","white","#ff5858"))
blue.colors  <- colorRampPalette(c("gray70","gray90","#56CCF2","#2F80ED","#0575E6"))

```

Load in event boundaries  
```{r}

# create event boundary windows
my.TR = 2.47
nTime = 193 #total number of movie TRs
boundaries <- read.csv('../../../behavioral-data/CamCan_movie_event_onsets_corrected.csv')  # from Ben-Yakov & Henson (2018) - updated Nov 2020
boundaries$TR <- boundaries$Boundary/my.TR

# I am now classifying time points as in (1) or outside (0) of an event transition window,
# with a window centered on each boundary
# test the effect of window size
window_TR = 2

boundary.windows <- array(0,c(nTime))
boundaries$adjustedTR <- round(boundaries$TR + 2)  #accounting for HRF lag (~5s) before rounding to nearest TR
for (b in 1:nrow(boundaries)){
  min.point <- boundaries$adjustedTR[b] - window_TR
  max.point <- boundaries$adjustedTR[b] + window_TR
  boundary.windows[min.point:max.point] <- 1
}


### option to re-define nTime if we only want to analyze up to a certain point. 
### added to check the influence of the "gun shot" event toward the end of the movie (no change to results)  
#nTime = 162
boundary.windows <- boundary.windows[1:nTime]

cat('Analyzing PMN connectivity over',nTime,'TRs (',round(nTime*my.TR,2),'seconds ) of movie watching\n')

```

# Data Inspection  

## ROI time series  
Mean (across voxels) time series from unsmoothed data  
```{r, fig.width = 6, fig.height = 4}

timeseries.file <- paste('../submission-orig/',this.group,'/PM_node_timeseries_',this.group,'.csv',sep="")
cat('Loading PMN time series from:',timeseries.file,'\n')


allData = read.csv(timeseries.file, header = TRUE)
# for testing -- analyze subset of time points
allData <- subset(allData, Time <=nTime)


allData$Subject=as.factor(allData$Subject)
allData$Node=as.factor(allData$Node)

subjects <- levels(allData$Subject)
NSubs    <- length(subjects)
cat('Total Number of Subjects =',NSubs,'\n')

rois = levels(allData$Node)
cat('ROIs =',rois,'\n')

# number of unique connections for 8x8 rois
nConnections <- ((length(rois)*length(rois)) - length(rois))/2

```

To facilitate data inspection, here is an interactive plot showing the denoised, mean time series of each ROI per subject.  
Each time series has been standardized within subject and ROI.  
```{r}

scaled_data <- allData %>% group_by(Subject, Node) %>%
                   mutate(Z = scale(Value))

lim <- ceil(max(abs(scaled_data$Z)))

plot_ly(scaled_data, x = ~Time, y = ~Z, frame = ~Subject, color = ~Node,
        colors = mycolors, type = "scatter", mode = "lines",
        width = 900, height = 400) %>%
  layout(title = "Z scored PM time series",
         xaxis = list(title = "TR"),
         yaxis = list(range = c(-lim,lim)))  %>%
  animation_opts(frame = 500, transition = 100, redraw = FALSE)

```

Mean standardized time series across subjects, by ROI:  
```{r, fig.width = 12, fig.height = 5}

summary_timeseries <- scaled_data %>% group_by(Time, Node) %>%
                         summarise(MeanZ = mean(Z),
                                   SEZ = se(Z))

ggplot(summary_timeseries) +
  scale_fill_manual(values = mycolors) +
  scale_color_manual(values = mycolors) +
  geom_hline(yintercept=0, size=1) +
  geom_ribbon(alpha=0.3, aes(x=Time*my.TR, fill=Node,
                             ymin=MeanZ-SEZ, ymax=MeanZ+SEZ), color=NA) +
  geom_line(aes(x=Time*my.TR, y=MeanZ, color=Node), size=1.5) +
  scale_y_continuous(expand=c(0,0.01,0,0), limits=c(-2,2.5)) +
  scale_x_continuous(expand=c(0,0,0,0)) +
  labs(x="Time (seconds)", y='Mean Z') +
  ggtitle('Group-averged ROI time-series') +
  theme(plot.title = element_text(size = 30, face='plain', hjust=0.5),
        axis.line.x = element_line(color = "black", size = 1),
        axis.line.y = element_line(color = "black", size = 1),
        axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 18),
        axis.title.y = element_text(size = 22), axis.title.x = element_text(size = 22),
        panel.background = element_blank(),
        legend.title = element_blank(),
        legend.key.size = unit(2,"line"),
        legend.margin = margin(0,0,0,0, "cm"),
        plot.margin = margin(0.25, 0.25, 0.25, 0.25, "cm"))

```

## Framewise displacement  
Even though FD, and other confounds, have been removed from the above ROI time series, here's the TR-by-TR FD for reference:  
```{r, fig.width = 12, fig.height = 5}

fdData = read.csv('../../../dataset-info/FD_byTR.csv', header = TRUE)

# filter by subjects in this sample:
fdData <- fdData[fdData$SubID %in% subjects,] %>% 
               droplevels()
fdData$SubID=as.factor(fdData$SubID)
colnames(fdData)[2] <- 'Time'

fdData <- subset(fdData, Time <= nTime)


summary_FD <- fdData %>% group_by(Time) %>%
                         summarise(Mean = mean(FD),
                                   SE = se(FD))

ggplot(summary_FD) +
  geom_ribbon(alpha=0.3, aes(x=Time*my.TR, ymin=Mean-SE, ymax=Mean+SE), 
              color=NA, fill="gray40") +
  geom_line(aes(x=Time*my.TR, y=Mean), size=1.5, color="gray20") +
  scale_y_continuous(expand=c(0,0,0,0), limits=c(0,.24)) +
  scale_x_continuous(expand=c(0,0,0,0)) +
  labs(x="Time (seconds)", y='Mean FD') +
  ggtitle('Group-averged FD') +
  theme(plot.title = element_text(size = 30, face='plain', hjust=0.5),
        axis.line.x = element_line(color = "black", size = 1),
        axis.line.y = element_line(color = "black", size = 1),
        axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 18),
        axis.title.y = element_text(size = 22), axis.title.x = element_text(size = 22),
        panel.background = element_blank(),
        legend.title = element_blank(),
        legend.key.size = unit(2,"line"),
        legend.margin = margin(0,0,0,0, "cm"),
        plot.margin = margin(0.25, 0.25, 0.25, 0.25, "cm"))

```

# Seed-to-voxel connectivity
Whole-brain data was smoothed (6mm FWHM) and masked with the MNI brainmask from normalization. 
Calculates the top 20% (range 30-10%) of voxel connections for each ROI.  
Note. Whole-brain connectivity was calculated in MATLAB, and is loaded in here as a csv file and pre-generated BrainNet Viewer images.  
```{r}

th_WB = 0.80 #top 20 % of connections -- for visualization
# also iterate over other roi-specific network densities to check the stability of communities
wb_iter = seq(from=.7, to=.9, by=.05) # 30% to 10% network densitiies


# read in csv with group-averaged seed-to-voxel connectivity patterns (r values)
seedtovoxel.file <- paste('../submission-orig/',this.group,'/wholebrain/group-average/group_PM_wholebrain_connectivity.csv',sep="")
cat('Loading seed-to-voxel connectivity values from:',seedtovoxel.file,'\n')
roi_wholebrain   <- read.csv(seedtovoxel.file)


# order columns by my roi order (currently alphabetical):
ord = match(rois,colnames(roi_wholebrain))
roi_wholebrain <- roi_wholebrain[,ord]

# store binarized whole brain connections (from group-level averaged connectivity) per seed, per density threshold
wholebrain_th <- array(NA,c(nrow(roi_wholebrain),ncol(roi_wholebrain),length(wb_iter)))
colnames(wholebrain_th) <- rois
for (d in 1:length(wb_iter)) {
  for (r in 1:length(rois)) {
    th <- quantile(roi_wholebrain[,r],wb_iter[d])
    wholebrain_th[roi_wholebrain[,r] >= th,r,d] <- 1
    wholebrain_th[roi_wholebrain[,r] < th,r,d]  <- 0
  }
}

# plot pre-generated images of each roi's top 20% of connections:  
plots.images = list()
for (r in 1:length(rois)) {
  plots.images[[r]] <- ggdraw() +
                       draw_image(paste('../submission-orig/',this.group,'/wholebrain/group-average/task-movie_',rois[r],
                                        '_R_seedtovoxel_binarized_quantile_',th_WB,'.png',sep="")) + 
                       ggtitle(rois[r]) +
                       theme(plot.title = element_text(hjust = 0.5, size=20, margin=margin(0,0,5,0)),
                             plot.margin = margin(0, 0, 0, 0, "cm"))
}

```

Now, I am using the Louvain method to detect ROI clusters based on the similarity of whole-brain connectivity patterns.  

* Default gamma = 1 -- using a range of values and then taking the % of iterations that each pair of ROIs is placed into the same module.  
* Group with hierarchical clustering (hclust).   
```{r}

gammas = seq(0.75,1.25,0.01) #default Louvain gamma = 1

group_modules <- data.frame(array(0,c(length(gammas)*length(wb_iter),length(rois))))
colnames(group_modules) <- rois

n = 0
# Calculate Louvain modules over densities...
for (d in 1:length(wb_iter)) {
  # correlate wholebrain seed-to-voxel connectivity patterns between rois
  net <- cor(wholebrain_th[,,d])

  # ... and gammas
  for (g in gammas) {
    n = n+1
    modules <- louvain(net,g)$community
    group_modules[n,] <- modules
  }
} # end of loop over densities


# calculate % of the time each ROI is grouped with every other (across all density + gamma levels):
roi_modules <- array(0,c(length(rois),length(rois)))
colnames(roi_modules) <- rois
rownames(roi_modules) <- rois
for (x in 1:length(rois)) {
  x_vec <- group_modules[,colnames(group_modules) == rois[x]]
  for (y in 1:length(rois)) {
    y_vec <- group_modules[,colnames(group_modules) == rois[y]]
    xy <- x_vec == y_vec
    roi_modules[x,y] <- (sum(xy)/length(x_vec))*100
  }
}



### plot ------
my.modules <- as.vector(group_modules[30,]) # manually selecting the best parcellation after visual inspection of clustering
n.mod <- max(unique(my.modules))



########## difference between discovery and replication markdowns #########
if (this.group == "Discovery") {
  # sort by communities
  ord = c()
  for (n in 1:n.mod) {
    idx <- which(my.modules == n)
    
    #hclust within module in case any more fine-grained module groupings
    h <- hclust(as.dist(100-roi_modules[idx,idx]))
    ord <- c(ord, idx[h$order])
  }
  
  # save this roi order for use with replication ample
  save(ord, file='roi_order.RData')
  
} else if (this.group == "Replication") {
  # load in ROI order from discovery sample to keep visualization consistent
  load('roi_order.RData')  
}
############################################################################



# ***** re-order by community ******* #
roi_modules  <- roi_modules[ord,ord]
my.modules   <- my.modules[ord]
allData$Node <- factor(allData$Node,levels(allData$Node)[ord])
mycolors     <- mycolors[ord]
rois         <- rois[ord]
# *********************************** #


# plot module matrix
data <- melt(roi_modules)
# remove diagonal
data <- data[data$Var1 != data$Var2,]

p2 <- ggplot(data, aes(Var1, Var2, fill=value)) +
  geom_tile(color="white", size=.5) +
  geom_text(aes(label = round(value)), size = 4, color="white") +
  scale_fill_gradientn(limits=c(40,100), colors = gray.colors(12), na.value = "white",
                       guide = guide_colorbar(frame.colour = "black")) +
  geom_rect(xmin=.5, xmax=length(rois)+.5, ymin=.5, ymax=length(rois)+.5,
            fill=NA, color="black",size=1) +
  geom_segment(aes(x = 0.5, y = 0.5, xend = 5.5, yend = 0.5), color = module.colors[1], size=4) +
  geom_segment(aes(x = 5.5, y = 0.5, xend = 8.5, yend = 0.5), color = module.colors[2], size=4) +
  geom_segment(aes(x = 0.5, y = 0.5, xend = 0.5, yend = 5.5), color = module.colors[1], size=4) +
  geom_segment(aes(x = 0.5, y = 5.5, xend = 0.5, yend = 8.5), color = module.colors[2], size=4) +
  labs(fill="% Same\nModule", tag="b") +
  ggtitle('Community probability')+
  theme(plot.title = element_text(hjust = 0.5, size=24, margin=margin(0,0,20,0), face="plain"),  
        axis.text.x = element_text(size = 16, color = mycolors, hjust=1, vjust=1, angle=45), 
        axis.text.y = element_text(size = 16, color = mycolors),
        axis.ticks.x = element_blank(),axis.ticks.y = element_blank(),
        axis.line.x = element_blank(),axis.line.y = element_blank(),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        legend.title = element_text(size=14), legend.text = element_text(size=12),
        legend.key.width = unit(0.4,"cm"), legend.key.height = unit(0.8,"cm"),
        plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.tag = element_text(size = 34, face = "bold"))


# add images showing overlap of connections by submodule
p3 <- ggdraw() +
  draw_image(paste('../submission-orig/',this.group,'/wholebrain/group-average/task-movie_quantile_',th_WB,'_sum_DorsalPM.png',sep="")) +
  ggtitle('"Dorsal PM": 20% density') + labs(tag="c") +
  geom_label(aes(x=0.5, y=0.065, label="Connected Regions"),
             size=4.5, color="black", fill="white", label.size=0) +
  geom_label(aes(x=0.5, y=0.115, label="0                        5"),
             size=4, color="black", fill=NA, label.size=0) +
  theme(plot.title = element_text(hjust = 0.5, size=24, margin=margin(0,0,10,0)),
        plot.tag = element_text(size = 34, face="bold"),
        plot.margin = margin(0, 0, 0, 0, "cm"))

p4 <- ggdraw() +
  draw_image(paste('../submission-orig/',this.group,'/wholebrain/group-average/task-movie_quantile_',th_WB,'_sum_VentralPM.png',sep="")) +
  ggtitle('"Ventral PM": 20% density') + labs(tag="d") +
  geom_label(aes(x=0.5, y=0.065, label="Connected Regions"),
             size=4.5, color="black", fill="white", label.size=0) +
  geom_label(aes(x=0.5, y=0.115, label="0                        3"),
             size=4, color="black", fill=NA, label.size=0) +
  theme(plot.title = element_text(hjust = 0.5, size=24, margin=margin(0,0,10,0)),
        plot.tag = element_text(size = 34, face="bold"),
        plot.margin = margin(0, 0, 0, 0, "cm"))

```

```{r, fig.width = 15, fig.height = 8}

# re-order panel A by module assignments and group:
p1 <- ggarrange(plotlist=plots.images[ord], ncol = 8, nrow = 1) +
          labs(tag="a") + theme(plot.tag = element_text(size = 34, face="bold"),
                                plot.margin = margin(0, 0, 0, 0, "cm"))

###### combine whole brain plots
p <- ggarrange(p2,p3,p4, ncol = 3, nrow = 1, widths=c(1.05,1,1))
myPlot <- ggarrange(p1,p, ncol = 1, nrow = 2, heights=c(0.75,1))
plot(myPlot)


## save
ggsave(paste('./',this.group,'/figures/seed-to-voxel_',this.group,'.pdf',sep=""), plot = myPlot, device = "pdf", width=15, height=8, unit="in")

```

From now on, ROIs are sorted into the above modules -- 'Ventral PM' and 'Dorsal PM'.   

# Intranetwork functional connectivity   
Pearson's correlation between the time-series of PMM regions, per subject:    
```{r}

## create full pearson's correlation connectivity matrix --> pearson's r
connMatrix = array(data = 0, c(length(rois),length(rois),NSubs))
colnames(connMatrix) <- rois
rownames(connMatrix) <- rois

for (s in 1:NSubs) {
  
  subData   <- subset(allData, Subject == subjects[s])
  # from long to wide format
  subMatrix <- spread(subData, Node, Value)
  # correlations between ROI time series
  connMatrix[,,s] <- cor(subMatrix[,match(rois,colnames(subMatrix))])
  diag(connMatrix[,,s]) <- 0

} #end of loop through subjects


# store
node.bivariate <- connMatrix

### calculate mean for each connection across subjects, applying fisher z transformation before averaging, 
### with group-averaged values converted back to r
node.bivariate.mean  <- fisherz2r(apply(fisherz(node.bivariate), c(1,2), mean))

```

Functional connections as a graph - r > .2 (dark = top 50%): 
```{r}

scale.factor <- 5  #just to scale edge weights for visualization, no impact on stats
c.th = .2
###########


net <- node.bivariate.mean
net[net < c.th]  = 0  #remove low connections
c.upper = median(net[abs(net)>0]) #dark for top 50% of edges


#plot network, highlighting strong connections
net <- net*scale.factor
net <- network(net, directed = FALSE, ignore.eval = FALSE, names.eval = "weights")
network::set.edge.attribute(net, "color",
                            ifelse(net %e% "weights" > (c.upper*scale.factor), "gray30", "gray70"))
network.vertex.names(net) = rois
p <- suppressMessages(ggnet2(net, mode = "circle",
                 node.size = 11, node.color = mycolors,
                 label=TRUE, label.size=4.5,
                 edge.size = "weights", edge.color = "color",
                 layout.exp = 0.05) +
  scale_y_continuous(expand=c(.05,.05,.05,.05)) +
  scale_x_continuous(expand=c(.05,.05,.05,.05)) +
  theme(plot.title = element_text(hjust = 0.5, size=28, margin=margin(0,0,20,0), face="plain"), 
        plot.margin = margin(0.2, 0.8, 0.2, 0.2, "cm"),
        axis.line.x = element_blank(), axis.line.y = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank()))

p <- ggarrange(p) + 
      labs(tag="a") + 
      theme(plot.tag = element_text(size = 34, face="bold"),
            plot.margin = margin(0.2, 0.2, 0, 0.2, "cm")) +
      geom_text(aes(x=0.86, y=0.15), size=6, color = "gray70",
                label=paste('r > ',c.th,sep=""), fontface = "bold.italic") +
      geom_text(aes(x=0.88, y=0.08), size=6, color = "gray30",
                label='top 50%', fontface = "bold.italic")

```

Average functional connectivity within and between PMN subsystems:  
```{r}

# labels connections by module:
data.mod <- melt(node.bivariate)  #Var3 = Subject index
data.mod <- data.mod[data.mod$value != 0,] # remove diagonal
data.mod$Module = ''
data.mod$Module[data.mod$Var1 %in% rois[my.modules==1] & data.mod$Var2 %in% rois[my.modules==1]] <- 'Dorsal'
data.mod$Module[data.mod$Var1 %in% rois[my.modules==2] & data.mod$Var2 %in% rois[my.modules==2]] <- 'Ventral'
data.mod$Module[(data.mod$Var1 %in% rois[my.modules==1] & data.mod$Var2 %in% rois[my.modules==2]) |
                (data.mod$Var1 %in% rois[my.modules==2] & data.mod$Var2 %in% rois[my.modules==1])] <- 'Ventral-Dorsal'


# within-subject mean module connectivity (fisher z transformed)
data.summary.subject <- data.frame(
                          data.mod %>% 
                          group_by(Var3, Module) %>%
                          summarise(Strength = mean(fisherz(value)))
                          )


# plot subject-level averages
p1 <- ggplot(data.summary.subject, aes(x=Module, y=fisherz2r(Strength), fill=Module)) +
  scale_fill_manual(values = module.colors) +
  scale_color_manual(values = module.colors) +
  geom_point(aes(color=Module), size = 1.5, position=position_jitter(width = .15), alpha=.6) +
  geom_boxplot(size=1, width=.5, color="black", outlier.color=NA, alpha=.4) +
  geom_hline(yintercept = 0, size = 1) +
  scale_y_continuous(expand = c(0,0.01,0,0.01), limits=c(-.25,.77)) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 7)) +
  labs(y='Pearson R', tag="b") +
  theme(axis.line.x = element_line(color = "black", size = 1), axis.line.y = element_line(color = "black", size = 1),
        axis.text.x = element_text(size = 18),
        axis.text.y = element_text(size = 18),
        axis.title.y = element_text(size = 20), axis.title.x = element_blank(),
        panel.background = element_blank(),
        legend.position="none",
        plot.tag = element_text(size = 34, face="bold"),
        plot.margin = margin(0.2, 0.2, 0, 0.2, "cm"))

# annotage with significance (manual)
p1 <- p1 + geom_segment(aes(x = 1.05, y = 0.65, xend = 1.85, yend = 0.65),size=0.5) +
           geom_text(aes(x=1.45, y=0.66), size=10, label='*') + 
           geom_segment(aes(x = 1.05, y = 0.72, xend = 2.95, yend = 0.72),size=0.5) +
           geom_text(aes(x=2, y=0.73), size=10, label='*') + 
           geom_segment(aes(x = 2.15, y = 0.65, xend = 2.95, yend = 0.65),size=0.5) +
           geom_text(aes(x=2.55, y=0.66), size=10, label='*')


#### means and CIs per module
data.summary.group <- data.summary.subject %>% group_by(Module) %>%
                           summarise(Mean = mean(Strength),
                                     CI = ci(Strength))
kable(data.summary.group, format = "pandoc",
      caption = "Mean functional connectivity (z) within and between PM modules")


#### t-tests to validate whole-brain defined modules in terms of bivariate connectivity
# runs on each pair of modules
ts <- data.summary.subject %>%
            pairwise_t_test(
                Strength ~ Module, paired = TRUE, 
                p.adjust.method = "none",
                detailed=T
            )
kable(ts, format = "pandoc",
      caption = "Functional connectivity differences within and between PM modules")


### save out time-averaged module connectivity for episodic memory individual differences analyses
data.summary.subject$Var3 <- subjects[data.summary.subject$Var3] # add in actual subject IDs from indexes
timeaveraged.file <- paste('./',this.group,'/module-connectivity_',this.group,'.RData',sep="")
cat('\nSaving time-averaged module connectivity to:',timeaveraged.file,'\n')
save(data.summary.subject, file=timeaveraged.file)

```

Functional connectivity per ROI to each subsystem -- shows ROIs that separate most are Precuneus and PHC:  
```{r}

# labels connections by module:
data.mod <- melt(node.bivariate)  #Var3 = Subject index
data.mod <- data.mod[data.mod$value != 0,] # remove diagonal
data.mod$Network = ''
# group according to first ROI column:
data.mod$Network[data.mod$Var1 %in% rois[my.modules==1]] <- 'Dorsal'
data.mod$Network[data.mod$Var1 %in% rois[my.modules==2]] <- 'Ventral'


# within-subject mean module and roi connectivity (fisher z transformed)
data.summary.subject <- data.frame(
                          data.mod %>% 
                          group_by(Var3, Var2, Network) %>%
                          summarise(Strength = mean(fisherz(value)))
                          )

#### means and CIs per module/ROI
data.summary.group <- data.summary.subject %>% group_by(Var2, Network) %>%
                           summarise(Mean = mean(Strength),
                                     CI = ci(Strength))
kable(data.summary.group, format = "pandoc",
      caption = "Mean functional connectivity (z) per ROI and subsystem")


#### t-tests to validate whole-brain defined modules in terms of bivariate connectivity
# runs on each pair of modules
ts <- data.summary.subject %>%
           group_by(Var2) %>%
            rstatix::t_test(
                Strength ~ Network, paired = TRUE, 
                detailed=T
            )
ts$sig <- ''
ts$sig[ts$p < .05] = '*'

kable(ts, format = "pandoc",
      caption = "Functional connectivity differences by ROI")


# plot subject-level averages
p2 <- ggplot(data.summary.subject, aes(x=Var2, y=fisherz2r(Strength))) +
  scale_fill_manual(values = module.colors) +
  scale_color_manual(values = module.colors) +
  geom_point(aes(color=Network, fill=Network), size = 1, 
             position=position_jitterdodge(jitter.width = .15, dodge.width=.75),
             alpha=.6) +
  geom_boxplot(aes(fill=Network), size=1, width=.5, alpha=.4, 
               outlier.color=NA, color="black",
               position=position_dodge(.75)) +
  geom_text(data=ts, aes(y=0.7, label=sig), size=12) +
  geom_hline(yintercept = 0, size = 1) +
  scale_y_continuous(expand = c(0,0.01,0,0.01), limits=c(-.3,.77)) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 7)) +
  labs(y='Pearson R', tag="c") +
  theme(axis.line.x = element_line(color = "black", size = 1), axis.line.y = element_line(color = "black", size = 1),
        axis.text.y = element_text(size = 18),
        axis.text.x = element_text(size = 20, color = mycolors), 
        axis.title.y = element_text(size = 20), axis.title.x = element_blank(),
        panel.background = element_blank(),
        legend.position="top", legend.title = element_blank(),
        legend.text = element_text(size=18),
        legend.key.width = unit(1,"cm"), legend.key.height = unit(1,"cm"),
        plot.tag = element_text(size = 34, face="bold"),
        plot.margin = margin(0, 0.5, 0, 0.2, "cm"))

```

Combine plots:  
```{r, fig.width = 9, fig.height = 9.5}

myPlotA <- ggarrange(p,p1, ncol = 2, widths=c(1,1))
myPlot <- ggarrange(myPlotA, p2, nrow=2, heights=c(1,1))

# add annotation for network groupings
lineA = ggplot() + geom_segment(aes(x = 0, y = 0, xend = 1, yend = 0),
                           color = module.colors[1], size=3) + theme_blank() +
                      theme(plot.margin = margin(0, 0, 0, 3.5, "cm"),
                            panel.background = element_rect(fill = "transparent"),
                            plot.background = element_rect(fill = "transparent", color = NA))
lineB = ggplot() + geom_segment(aes(x = 0, y = 0, xend = 1, yend = 0),
                           color = module.colors[2], size=3) + theme_blank() +
                      theme(plot.margin = margin(0, 1, 0, 0, "cm"),
                            panel.background = element_rect(fill = "transparent"),
                            plot.background = element_rect(fill = "transparent", color = NA))

lines = ggarrange(lineA, lineB, ncol=2, widths= c(2.05,1))
myPlot <- ggarrange(myPlot, lines, nrow=2, heights=c(18,1))
plot(myPlot)



## save as Rdata for merging with other group
save(myPlot, file=paste('./',this.group,'/figures/intranetwork_',this.group,'.RData',sep=""))

```

## Virtual lesion (Supplemental)
Here, I'm testing the mediating influence of each node on other connections within the network -- if we partial out (remove) each node in turn rather than all at once (partial network, above), how do the other connections in the network change?

For each node, I'm generating a circular graph without that node and it's connections. The width of each edge represents the strength of the original connection (c in a mediation model). The color of the edge (from gray to blue) represents how much that connection has decreased after 'lesioning' a node (Pm = 1-[c'/c], where c' is the partial correlation in a mediation model). [Pm = proportion mediated]  
```{r}

### group-level bivariate mask -- 
### only plot connections originally > threshold for visualization
### (to make sure there is something meaningful to mediate)
b.mask <- node.bivariate.mean
b.mask[b.mask < c.th] <- 0
b.mask[b.mask > 0] <- 1
diag(b.mask) <- 0

# color gradient of edge colors to show % connection strength mediated
edge.bins    <- seq(.1,1,by=.1) # increments of Pm
edge.colors  <- blue.colors(length(edge.bins))
# ---------------------------------------------------------------------# 


# to store summary network Pm stats:
roi_effect = data.frame(array(0,c(length(rois)*NSubs,3)))
colnames(roi_effect) = c('SubID','Node','Influence')
row = 0

# to store partial networks after removing RSC and PCC, to illustrate strongest effects
lesion.examples <- array(data = NA, c(length(rois),length(rois),2))
ex = 0


plots.graphs = list()
for (p in 1:length(rois)) {
  #for full bivariate (ignoring this node's connections)
  connMatrix.c = array(data = NA, c(length(rois),length(rois),NSubs))
  colnames(connMatrix.c) <- rois
  rownames(connMatrix.c) <- rois
  #for partial (removing mediating influence of this roi)
  connMatrix.p <- connMatrix.c  

  for (s in 1:length(subjects)) {
    subData <- subset(allData, Subject == subjects[s])
    #time-series for this node (mediator)
    pData   <- subData$Value[subData$Node == rois[p]] 
    
    for (y in 1:length(rois)) {
      #time-series for ROIy
      yData = subData$Value[subData$Node == rois[y]]
      for (x in 1:length(rois)) {
        # time-series for ROIx
        xData = subData$Value[subData$Node == rois[x]]
        if ((y != p) & (x != p) & (x != y)) {
          # partial correlation between x and y when controlling for p
          connMatrix.p[y,x,s] <- pcor(cbind(xData,yData,pData))$estimate["xData","yData"]
          # original, bivariate correlation between x and y
          connMatrix.c[y,x,s] <- cor(xData,yData)
        }
      }
    }
    
    
    # per subject, what is the % of variance in all other connections accounted for? 
    # (% change from mean original PMN correlation to mean partial)
    row = row + 1
    roi_effect$SubID[row] <- s  #subject index
    roi_effect$Node[row]  <- rois[p]
    p.conn <- fisherz2r(mean(fisherz(connMatrix.p[,,s]), na.rm = TRUE)) # average partial correlation (c')
    c.conn <- fisherz2r(mean(fisherz(connMatrix.c[,,s]), na.rm = TRUE)) # average original correlation (c)
    Pm <- 1 - (p.conn/c.conn) # proportion mediated
    if (Pm < 0) { #mask any small "supressing" effects where average p.conn is actually larger than average c.conn
      Pm <- 0
    } else if (Pm > 1) { #if the average p.conn is now negative
      Pm <- 1
    }
    roi_effect$Influence[row] <- Pm

  } #end of loop through subjects


  ### calculate group-level Pm for each PMN connection ----------------------- #
  connmean.p <- fisherz2r(apply(fisherz(connMatrix.p), c(1,2), mean))
  ## store partial network for example plot if PCC or RSC
  if (rois[p] == "PCC" || rois[p] == "RSC") {
    ex = ex + 1
    lesion.examples[,,ex] <- connmean.p
  }
  connmean.p[b.mask == 0] <- NA #ignore connections that weren't present above our threshold (needs to be something to reduce)
  connmean.c <- fisherz2r(apply(fisherz(connMatrix.c), c(1,2), mean))
  connmean.c[b.mask == 0] <- NA
  
  # pm for each connection
  connmean.r <- 1 - (connmean.p/connmean.c)
  connmean.r[connmean.r < 0] <- 0.001 #mask for edges where there is a small increase for partial cor ("supressing" effects)
  # ^^ setting non-zero just so it gets recognized as an edge below
  connmean.r[connmean.r > 1] <- 1     #where p.conn is now negative, all variance in c.conn is explained. 

  

  ##### PLOT ---------------------------------------------------------------- #

  #specify initial network of variance explained (Pm) to get edge colors
  net <- connmean.r
  net[is.na(net)] <- 0
  net <- network(net, directed = FALSE, ignore.eval = FALSE, names.eval = "weights")

  # set gradient color for % reduction per edge
  my.edges     <- network::get.edge.value(net, "weights")
  edge.colors.sort <- array('',c(length(my.edges)))
  for (e in 1:length(my.edges)) {
    diff <- edge.bins - my.edges[e]
    diff[diff < 0] = 2  #set above max to get next lowest bin
    edge.colors.sort[e] <- edge.colors[diff == min(diff)]
  }
  # if it's the first mediator ROI, get a color scale to later add to the plot:
  if (p == 1) {
    net.df <- ggnetwork(net, layout="circle")
    edge.p <- ggplot(net.df, aes(x = x, y = y, xend = xend, yend = yend,
                            color=weights)) +
      geom_edges() +
      scale_color_gradientn(limits = c(min(edge.bins),max(edge.bins)),
                            colors  = edge.colors, na.value = "white",
                            guide = guide_colorbar(frame.colour = "black")) +
      labs(color="Proportion\nmediated") +
      theme(legend.text = element_text(size=16), 
            legend.title = element_text(size=18, margin = margin(0,0,5,0)),
            legend.key.width = unit(0.4,"cm"), legend.key.height = unit(1,"cm"),
            plot.margin = margin(0, 0.25, 0, 0, "cm"))
    edge.legend <- as_ggplot(get_legend(edge.p))
  }
  
  
  #now replace network with the original bivariate connections (for edge width)
  net <- connmean.c*6  #scale just for visualization purposes
  net[is.na(net)] <- 0
  net <- network(net, directed = FALSE, ignore.eval = FALSE, names.eval = "weights")
  
  # draw graph
  # make current node white so not visible (removed statistically)
  lesion.colors <- mycolors
  lesion.colors[p] <- "white" #remove current mediator node
  network.vertex.names(net) = rois
  plots.graphs[[p]] <- suppressMessages(ggnet2(net, mode = "circle",
                              node.size = 10, node.color = lesion.colors,
                              label=FALSE,
                              edge.size = "weights", edge.color = edge.colors.sort,
                              layout.exp = 0.05) +
    scale_y_continuous(expand=c(.05,.05,.05,.05)) +
    scale_x_continuous(expand=c(.05,.05,.05,.05)) +
    theme(plot.margin = margin(0.25, 0.5, 1, 0.5, "cm"),
          plot.title = element_text(size = 28, margin=margin(5,0,10,0), face="plain", hjust=0),
          axis.line.x = element_blank(), axis.line.y = element_blank(),
          axis.text.y = element_blank(), axis.ticks.y = element_blank(),
          axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
    ggtitle(rois[p]) + border(size = 1.5, linetype = 1))


}  # end of loop through mediator rois ---------------------------------------------- #

```

Proportion of network connectivity mediated, by ROI:
```{r}

## Add summary node influence bar graph ---------------------------------------
roi_effect$Node <- as.factor(roi_effect$Node)
roi_effect$Node <- factor(roi_effect$Node,levels(roi_effect$Node)[ord])
roi_effect.summary <- roi_effect %>%
                       group_by(Node) %>%
                       summarise(Strength = mean(Influence), CI = ci(Influence))

# now reorder rois (and their colors) by mean mediating effect for these plots
med.ord    <- order(roi_effect.summary$Strength)
med.rois   <- rois[med.ord]
med.colors <- mycolors[med.ord]
roi_effect$Node <- factor(roi_effect$Node,levels(roi_effect$Node)[med.ord])


### plot average influence per roi:
p1 <- ggplot(roi_effect, aes(x=Node, y=Influence, color=Node, fill=Node)) +
     scale_fill_manual(values = med.colors) +
     scale_color_manual(values = med.colors) +
     geom_point(size = 2, position=position_jitter(width = .1), alpha=.6) +
     geom_boxplot(size=1, width=.5, color="black", outlier.color=NA, alpha=.4) +
     scale_y_continuous(expand = c(0,0,0,0), limits=c(-.01,1.01)) +
     labs(y='Network Pm', tag="c") +
     theme(axis.line.x = element_line(color = "black", size = 1),
          axis.line.y = element_line(color = "black", size = 1),
          axis.text.x = element_text(size = 22, hjust=1, vjust=1, angle=45),
          axis.text.y = element_text(size = 20),
          axis.title.y = element_text(size = 22), axis.title.x = element_blank(),
          panel.background = element_blank(),
          legend.position="none",
          plot.tag = element_text(size = 40, face="bold"),
          plot.margin = margin(0.25, 0.5, 0.25, 0, "cm"))

```

Illustrate the resulting network (thresholded at r > .2) if you remove RSC or PCC (largest Pm):  
```{r}

lesion.examples[is.na(lesion.examples)] <- 0
lesion.examples[lesion.examples < c.th] <- 0  #remove low correlations


### RSC
net <- lesion.examples[rois!="RSC",rois!="RSC",2]
net <- network(net, directed = FALSE, ignore.eval = FALSE, names.eval = "weights")

# draw graph
network.vertex.names(net) = rois[rois!="RSC"]
p.lesionA <- suppressMessages(ggnet2(net,
                    node.size = 8, node.color = mycolors[rois!="RSC"],
                    label=FALSE,
                    edge.size = 2, edge.color = "gray70",
                    layout.exp = 0.1) +
  scale_y_continuous(expand=c(.05,.05,.05,.05)) +
  theme(plot.margin = margin(0, 0.5, 0, 3, "cm"),
        axis.text.y = element_blank(), axis.ticks.y = element_blank()) +
  border(size = 2, linetype = 1, color=mycolors[rois=="RSC"]))


### PCC
net <- lesion.examples[rois!="PCC",rois!="PCC",1]
net <- network(net, directed = FALSE, ignore.eval = FALSE, names.eval = "weights")

# draw graph
network.vertex.names(net) = rois[rois!="PCC"]
p.lesionB <- suppressMessages(ggnet2(net,
                    node.size = 8, node.color = mycolors[rois!="PCC"],
                    label=FALSE,
                    edge.size = 2, edge.color = "gray70",
                    layout.exp = 0.1) +
  scale_y_continuous(expand=c(.05,.05,.05,.05)) +
  theme(plot.margin = margin(0, 1, 0, 0.5, "cm"),
        axis.text.y = element_blank(), axis.ticks.y = element_blank()) +
  border(size = 2, linetype = 1, color=mycolors[rois=="PCC"]))


# join
p.lesion <- ggarrange(p.lesionA,p.lesionB, ncol=2, widths=c(1.32,1)) +
            labs(tag="b") + theme(plot.tag = element_text(size = 40, face="bold"))

```

```{r, fig.width = 19, fig.height = 7.5}

# order and plot graph panels:
myPlot <- ggarrange(plotlist=plots.graphs[med.ord], ncol = 4, nrow = 2) +
          labs(tag="a") + theme(plot.tag = element_text(size = 40, face="bold"))

# add lesion examples over summary plot
myPlotB <- ggarrange(p.lesion, p1, nrow=2, heights=c(2,5))

# join! (with edge color legend)
joined.Plot <- ggarrange(myPlot, edge.legend, myPlotB, ncol=3, nrow=1, widths=c(2,0.25,1))
plot(joined.Plot)

## save as Rdata for merging with other group
save(joined.Plot, file=paste('./',this.group,'/figures/virtual-lesion_',this.group,'.RData',sep=""))

```
 
# Movie-related connectivity  
The following analyses test time-varying connectivity in relation to the movie content, first by testing changes in connectvity at event transitions and, second, by testing the similarity of PMN connectivity fluctuations across subjects.  

## Event transitions  
This analysis uses logistic regression to test how an edge time-series (interaction) changes at event transitions -- do PMN regions become more in sync when event context shifts?  
Edge time series are calculated using the product of the zscored activity time series.   
```{r}

## create full matrix for modulation
connMatrix = array(data = 0, c(length(rois),length(rois),NSubs))
colnames(connMatrix) <- rois
rownames(connMatrix) <- rois

for (s in 1:NSubs) {
  subData <- subset(allData, Subject == subjects[s])
  subMatrix <- spread(subData, Node, Value)
  subMatrix$Event <- boundary.windows

  for (x in 1:length(rois)) {
    for (y in 1:length(rois)) {
      if (x > y) {
        test_cols <- c("Event",rois[c(x,y)])
        sub_test_data <- subMatrix[,match(test_cols,colnames(subMatrix))]
        colnames(sub_test_data)[2:3] <- c('ROIx','ROIy')

        # z score roi time-series:
        sub_test_data[,2:3] <- scale(sub_test_data[,2:3])

        # store relationship (beta)
        this.model <- summary(glm(Event ~ ROIx*ROIy, family = "binomial", data = sub_test_data))
        connMatrix[x,y,s] <- this.model$coefficients["ROIx:ROIy","Estimate"]
      }
    }
  }
} #end of loop through subjects


### calculate mean and p-value for each modulation ----------------------- #
meanconn <- apply(connMatrix, c(1,2), mean)


# mirror for symmetrical matrix
meanconn[upper.tri(meanconn, diag = FALSE)] <- t(meanconn)[upper.tri(meanconn, diag = FALSE)]


### PLOT #### ------------------------------------------------------------ #
data = melt(meanconn)
data <- data[data$Var1 != data$Var2,] #remove diagonal
p <- ggplot(data, aes(Var1, Var2, fill=value, color=value)) +
  geom_tile() +
  scale_fill_gradientn(limits= c(-.25,.25),
                       colors = heat.colors(10), na.value = "white",
                       guide = guide_colorbar(frame.colour = "black")) +
  scale_color_gradientn(limits= c(-.25,.25),
                        colors = heat.colors(10), na.value = "white") +
  labs(fill="Beta", tag="a") +
  guides(color=FALSE) +
  geom_rect(xmin=.5, xmax=length(rois)+.5, ymin=.5, ymax=length(rois)+.5,
              fill=NA, color="black",size=1) +
  geom_segment(aes(x = 0.5, y = 0.5, xend = 5.5, yend = 0.5), color = module.colors[1], size=5) +
  geom_segment(aes(x = 5.5, y = 0.5, xend = 8.5, yend = 0.5), color = module.colors[2], size=5) +
  geom_segment(aes(x = 0.5, y = 0.5, xend = 0.5, yend = 5.5), color = module.colors[1], size=5) +
  geom_segment(aes(x = 0.5, y = 5.5, xend = 0.5, yend = 8.5), color = module.colors[2], size=5) +
  theme(axis.text.x = element_text(size = 18, hjust=1, vjust=1, angle=45, color = mycolors),
        axis.text.y = element_text(size = 18, color = mycolors),
        axis.line.x = element_blank(),axis.line.y = element_blank(),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        panel.grid.major=element_blank(),
        legend.text = element_text(size=16),legend.title = element_text(size=18),
        legend.key.width = unit(0.5,"cm"), legend.key.height = unit(1,"cm"),
        plot.tag = element_text(size = 32, face="bold"),
        plot.margin = margin(0.2, 0.1, 0.5, 0.1, "cm"))

```

Event modulation of connectivity within and between modules:
```{r}

### mean modulation by module -------------------------------------------
# add module IDs (within-Ventral, within-Dorsal, Ventral-Dorsal)
data.mod = melt(connMatrix)  #Var3 = subject
data.mod <- data.mod[data.mod$value != 0,]  # remove upper triangle
data.mod$Module = ''
data.mod$Module[data.mod$Var1 %in% rois[my.modules==1] & data.mod$Var2 %in% rois[my.modules==1]] <- 'Dorsal'
data.mod$Module[data.mod$Var1 %in% rois[my.modules==2] & data.mod$Var2 %in% rois[my.modules==2]] <- 'Ventral'
data.mod$Module[(data.mod$Var1 %in% rois[my.modules==1] & data.mod$Var2 %in% rois[my.modules==2]) |
                (data.mod$Var1 %in% rois[my.modules==2] & data.mod$Var2 %in% rois[my.modules==1])] <- 'Ventral-Dorsal'

### store this modulation for correlations with structural
event.pmn.connectivity <- data.mod


data.summary.subject <- data.frame(
                         data.mod %>% group_by(Var3, Module) %>%
                         summarise(Strength = mean(value))
                         )

data.summary.group <- data.summary.subject %>% group_by(Module) %>%
                         summarise(Mean = mean(Strength),
                                   CI = ci(Strength))
kable(data.summary.group, format = "pandoc",
      caption = "Mean change in connectivity within and between PM modules at event transitions")


#### one-sample t-tests to test change in connectivity with event transitions
ts.plot <- data.summary.subject %>%
             group_by(Module) %>%
             rstatix::t_test(Strength ~ 1, mu=0,
                             p.adjust.method = "none",
                             detailed=T)
ts.plot$p.signif <- ''
ts.plot$p.signif[ts.plot$p < .05] <- '*'
kable(ts.plot, format = "pandoc",
      caption = "Event modulation of PM module connectivity")
ts <- data.summary.subject %>%
            pairwise_t_test(
                Strength ~ Module, paired = TRUE,
                p.adjust.method = "none")
kable(ts, format = "pandoc",
      caption = "Event modulation differences across PM modules")


### plot with significance
p2 <- ggplot(data.summary.subject, aes(x=Module, y=Strength, color=Module, fill=Module)) +
  scale_fill_manual(values = module.colors) +
  scale_color_manual(values = module.colors) +
  geom_point(size = 1.5, position=position_jitter(width = .15), alpha=.6) +
  geom_boxplot(size=1, width=.5, outlier.color=NA, color="black", alpha=.4) +
  geom_text(data=ts.plot, aes(y=.7, label=p.signif), color="black", size = 12) +
  geom_hline(yintercept = 0, size = 1) +
  scale_y_continuous(expand = c(0.02,0.02,0.02,0.02), limits=c(-.45,.75)) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 7)) +
  labs(y='Beta', tag="b") +
  theme(axis.line.x = element_line(color = "black", size = 1), axis.line.y = element_line(color = "black", size = 1),
        axis.text.x = element_text(size = 18),
        axis.text.y = element_text(size = 18),
        axis.title.y = element_text(size = 20),
        axis.title.x = element_blank(), panel.background = element_blank(),
        legend.position="none",
        plot.tag = element_text(size = 32, face="bold"),
        plot.margin = margin(0.2, 0.2, 1, 0, "cm"))


# ---------------------------------------------------------- #
plot.A <- ggarrange(p,p2, ncol = 2, nrow = 1, widths = c(3.75,3))

```

Time-varying connectivity:

* This analysis uses a sliding-window of 25 TRs (2.47s TR, ~ 60s) to estimate a connectivity matrix at each time point, per subject. Below, I'm first plotting the mean bivariate connectivity of the Ventral PM, Dorsal PM, and Ventral-to-Dorsal connections over time.  
* I calculate connectivity at each time point with spearman correlation to avoid the strong influence of extreme values with a small window size.  
* Gray windows indicate event transitions for visualization.  
```{r}

# sliding window (TRs)
window = 25


# store time-varying connectivity in long format
TV.module.connectivity <- data.frame(array(0,c(NSubs*nTime*3,4)))
colnames(TV.module.connectivity) <- c('Subject','Time','Module','Conn')

n.row = 0
for (s in 1:NSubs) {
  subData <- subset(allData, Subject == subjects[s])
  sub.timeseries <- spread(subData, Node, Value)

  for (t in 1:nTime) {
    # get time window for this TR
    TR.min <- t-((window-1)/2)
    TR.max <- t+((window-1)/2)
    if (TR.min < 1){ TR.min = 1 }
    if (TR.max > nTime){ TR.max = nTime }

    sub.window <- subset(sub.timeseries, Time >= TR.min & Time <= TR.max)
    sub_cors   <- cor(sub.window[,match(rois,colnames(sub.window))], method="spearman")
    diag(sub_cors)  <- NA

    # now calculate mean time-varying connectivity by module
    sub_cors <- melt(sub_cors)
    sub_cors$Module = ''
    sub_cors$Module[sub_cors$Var1 %in% rois[my.modules==1] & sub_cors$Var2 %in% rois[my.modules==1]] <- 'Dorsal'
    sub_cors$Module[sub_cors$Var1 %in% rois[my.modules==2] & sub_cors$Var2 %in% rois[my.modules==2]] <- 'Ventral'
    sub_cors$Module[(sub_cors$Var1 %in% rois[my.modules==1] & sub_cors$Var2 %in% rois[my.modules==2]) |
                      (sub_cors$Var1 %in% rois[my.modules==2] & sub_cors$Var2 %in% rois[my.modules==1])] <- 'Ventral-Dorsal'

    module.means <- sub_cors %>% group_by(Module) %>%
                         summarise(Conn = mean(value, na.rm=TRUE))

    my.rows <- (n.row+1):(n.row+nrow(module.means))
    TV.module.connectivity$Subject[my.rows] <- as.character(subjects[s])
    TV.module.connectivity$Time[my.rows]    <- t
    TV.module.connectivity$Module[my.rows]  <- module.means$Module
    TV.module.connectivity$Conn[my.rows]    <- module.means$Conn
    n.row <- n.row+nrow(module.means)
  }
} #end of loop through subjects


# mean across subjects ---------------- #
TV.connectivity.mean <- TV.module.connectivity %>% group_by(Time,Module) %>%
                               summarise(Mean = mean(Conn),
                                         SE = se(Conn))


# plot with event boundary windows overlaid ------------------------------- #
# A) get transition boxes
b.df <- data.frame(boundary.windows)
b.df$Time <- 1:nTime
b.df <- subset(b.df, boundary.windows == 1)
b.groups = data.frame(array(0,c(nrow(b.df),2)))
colnames(b.groups) <- c('start','end')

ncl = 1
for (i in 1:nrow(b.df)) {
  if (i == 1) {
    # start of first cluster
    b.groups$start[ncl] <- b.df$Time[i]
  } else if (i == nrow(b.df)) {
    # final point = end of current cluster
    b.groups$end[ncl]   <- b.df$Time[i]
  } else if (b.df$Time[i] != b.df$Time[i-1]+1) {
    # if we have switched cluster, store end of last and start of current
    b.groups$end[ncl]   <- b.df$Time[i-1]
    ncl = ncl + 1
    b.groups$start[ncl] <- b.df$Time[i]
  }
}
b.groups <- b.groups[!c(b.groups$start == 0),]

# save b.groups -- event transition windows
save(b.groups, file="event_transitions.RData")


# B) plot
plot.B <- ggplot(TV.connectivity.mean) +
  geom_rect(data = b.groups, aes(xmin=start*my.TR, xmax=end*my.TR, ymin=-Inf,ymax=Inf),
            fill = 'gray90') +
  scale_fill_manual(values = module.colors) +
  scale_color_manual(values = module.colors) +
  geom_ribbon(alpha=0.3, aes(x=Time*my.TR, fill=Module,
                             ymin=Mean-SE, ymax=Mean+SE), color=NA) +
  geom_line(aes(x=Time*my.TR, y=Mean, color=Module), size=1.5) +
  scale_y_continuous(expand=c(0,0,0,0), limits=c(.1,.5)) +
  scale_x_continuous(expand=c(0,0,0,0)) +
  labs(x="Time (seconds)", y='Mean Connectivity', tag="c") +
  theme(axis.line.x = element_line(color = "black", size = 1),
        axis.line.y = element_line(color = "black", size = 1),
        axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 18),
        axis.title.y = element_text(size = 18), axis.title.x = element_text(size = 20),
        panel.background = element_blank(),
        legend.position="none", legend.title = element_blank(),
        plot.tag = element_text(size = 32, face="bold"),
        plot.margin = margin(0, 0.2, 0.2, 0.1, "cm"))


### save out vectors of TV connectivity to compare across groups
timevarying.file = paste('./',this.group,'/time-varying_',this.group,'.RData',sep="")
cat('Saving time-varying module connectivity to:',timevarying.file,'\n')
save(TV.module.connectivity, file=timevarying.file)

```

Combine Plots:  
```{r, fig.width = 10, fig.height = 8.5}

myPlot <- ggarrange(plot.A,plot.B, ncol = 1, nrow=2, heights=c(1.3,1))
plot(myPlot)

## save as Rdata for merging with other group
save(myPlot, file=paste('./',this.group,'/figures/event-modulation_',this.group,'.RData',sep=""))
```

### Activity replication (Supplemental)  
In line with Ben-Yakov & Henson (2018), here I'm plotting the mean change in activity from within-event time points to event boundaries to show replication of PMN sensitivity to changes in event context.    
```{r, fig.width = 8.5, fig.height = 7}

allData.events <- allData
allData.events$boundary <- rep(boundary.windows,nrow(allData)/nTime)

allData.events$boundary[allData.events$boundary == 0] <- "Within"
allData.events$boundary[allData.events$boundary == 1] <- "Transition"

# zscore time series within subject and node
allData.events <- allData.events %>%
                     group_by(Subject, Node) %>%
                        mutate(z = scale(Value))

events.summary <- allData.events %>% 
                    group_by(Subject, Node, boundary) %>%
                    summarise(Activity = mean(z)) %>%
                    spread(boundary, Activity) %>%
                    mutate(Difference = Transition - Within)

#### t-tests for change not 0, with FDR-correction across ROIs
ts.plot <- events.summary %>%
             group_by(Node) %>%
             rstatix::t_test(Difference ~ 1, mu=0,
                             p.adjust.method = "none",
                             detailed=T)
ts.plot$p.adj <- p.adjust(ts.plot$p, method="fdr")
ts.plot$p.signif <- ''
ts.plot$p.signif[ts.plot$p.adj < .05] <- '*'
kable(ts.plot, format = "pandoc",
      caption = "Change in PMN activity at event transitions")


### plot average change in activity per roi:
p <- ggplot(events.summary, aes(x=Node, y=Difference, color=Node, fill=Node)) +
  scale_fill_manual(values = mycolors) +
  scale_color_manual(values = mycolors) +
  geom_hline(yintercept = 0, size = 1) +
  geom_point(size = 1.5, position=position_jitter(width = .1), alpha=.6) +
  geom_boxplot(size=1, width=.6, color="black", outlier.color=NA, alpha=.4) +
  geom_text(data=ts.plot, aes(y=.74, label=p.signif), color="black", size = 16) +
  scale_y_continuous(expand = c(0.05,0.02,0.02,0.02), limits=c(-.5,.75)) +
  labs(y='Transition - Within Activity') +
  theme(axis.line.x = element_line(color = "black", size = 1),
        axis.line.y = element_line(color = "black", size = 1),
        axis.text.x = element_text(size = 26, hjust=1, vjust=1, angle=45),
        axis.text.y = element_text(size = 24),
        axis.title.y = element_text(size = 26), axis.title.x = element_blank(),
        panel.background = element_blank(),
        legend.position="none",
        plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm"))
plot(p)


## save as Rdata for merging with other group
save(p, file=paste('./',this.group,'/figures/event-activity_',this.group,'.RData',sep=""))

```

## Intersubject correlations
These analyses test the similarity of time-varying connectivity across subjects -- similarity should only occur if connectivity flutuations are related to the (shared) movie content.  
Calculates an intersubject correlation per subject (fisher-z transformed) using a leave-one-out approach -- correlation between Subject X and the mean time-varying connectivity of Subject !X  
```{r, fig.width=10, fig.height=5}

TV.cors <- data.frame(array(0,c(NSubs,4)))
colnames(TV.cors) <- c('Subject',unique(TV.module.connectivity$Module))


##### across-subject correlations
# Dorsal
TV.subset.Dorsal <- data.frame(subset(TV.module.connectivity, Module == "Dorsal") %>%
                      spread(Subject, Conn))
subj.cols <- 3:ncol(TV.subset.Dorsal)
for (s in 1:length(subjects)) {
  this.subj   <- TV.subset.Dorsal[,subj.cols[s]]
  other.subjs <- rowMeans(TV.subset.Dorsal[,subj.cols[-s]])
  TV.cors$Dorsal[s] <- fisherz(cor(this.subj, other.subjs))
}


# Ventral
TV.subset.Ventral <- data.frame(subset(TV.module.connectivity, Module == "Ventral") %>%
                      spread(Subject, Conn))
subj.cols <- 3:ncol(TV.subset.Ventral)
for (s in 1:length(subjects)) {
  this.subj   <- TV.subset.Ventral[,subj.cols[s]]
  other.subjs <- rowMeans(TV.subset.Ventral[,subj.cols[-s]])
  TV.cors$Ventral[s] <- fisherz(cor(this.subj, other.subjs))
}


# Ventral-to-Dorsal (both directions) - 
# does time-varying connectivity of the Dorsal subsystem correlate with time-varying connectivity of the Ventral subsystem across subjects? 
for (s in 1:length(subjects)) {
  this.subj   <- TV.subset.Ventral[,subj.cols[s]]
  other.subjs <- rowMeans(TV.subset.Dorsal[,subj.cols[-s]])
  cor.a <- fisherz(cor(this.subj, other.subjs))
  
  this.subj   <- TV.subset.Dorsal[,subj.cols[s]]
  other.subjs <- rowMeans(TV.subset.Ventral[,subj.cols[-s]])
  cor.b <- fisherz(cor(this.subj, other.subjs))
  
  TV.cors$`Ventral-Dorsal`[s] <- (cor.a + cor.b)/2
}



# reshape
TV.cors$Subject <- subjects
TV.cors <- TV.cors %>% pivot_longer(cols=c(-1), names_to="Type", values_to="Z")


### summarise and test against zero
ts <- TV.cors %>%
             group_by(Type) %>%
             rstatix::t_test(Z ~ 1, mu=0,
                             p.adjust.method = "none",
                             detailed=T)
kable(ts, format = "pandoc",
      caption = "Intersubject correlations of time-varying connectivity?")
cor.means <- data.frame(TV.cors %>% group_by(Type) %>% 
                         summarise(Mean=mean(Z), 
                                   SE=se(Z)))
pander(cor.means)  #mean and SE accross subjects



## plot distribution of within-subject and across-subject correlations -----------------------------
ggplot(TV.cors, aes(x=fisherz2r(Z), fill=Type, color=Type, group=Type)) +
  geom_density(adjust=1/2, alpha=.4, size=2) +
  scale_color_manual(values=module.colors) +
  scale_fill_manual(values=module.colors) +
  geom_vline(xintercept = 0, linetype=1, size=1) +
  geom_vline(data=cor.means, aes(xintercept = Mean[Type=="Dorsal"]), linetype=2, size=1.5, color=module.colors[1]) +
  geom_vline(data=cor.means, aes(xintercept = Mean[Type=="Ventral"]), linetype=2, size=1.5, color=module.colors[2]) +
  geom_vline(data=cor.means, aes(xintercept = Mean[Type=="Ventral-Dorsal"]), linetype=2, size=1.5, color=module.colors[3]) +
  scale_y_continuous(expand=c(0,0,0.01,0)) +
  scale_x_continuous(expand=c(0,0,0,0), limits=c(-1,1)) +
  ggtitle('Distribution of time-varying\nintersubject correlations') +
  labs(x="Intersubject Pearson R", y='Density') +
  theme(plot.title = element_text(size = 28, hjust=0.5, face="plain", margin=margin(0,0,40,0)),
        axis.line.x = element_line(color = "black", size = 1),
        axis.line.y = element_line(color = "black", size = 1),
        axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 20),
        axis.title.y = element_text(size = 22), axis.title.x = element_text(size = 22),
        panel.background = element_blank(), 
        legend.title = element_blank(),
        legend.key.width = unit(1,"cm"), legend.key.height = unit(1,"cm"),
        legend.text = element_text(size=18),
        plot.margin = margin(0.25, 0.25, 0.25, 0.25, "cm"))

```
